---
output: html_document
editor_options: 
  chunk_output_type: console
---

# CLIA

Laboratories that examine human specimens for the diagnosis, prevention, or
treatment of any disease or impairment of, or the assessment of the health of,
human beings are yet another category of suppliers and must meet Clinical
Laboratory Improvements of 1988 Act (CLIA) requirements. 

```{r setup}
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
source("code/gt_theme.R")
```

```{r}
#| label: api-clia
#| message: true
provider::clia(count = TRUE)
# provider::clia(ccn = provider::starts_with("11D0"))
```

## Examples

```{r}
parse("45D0501072")
decode("45D0501072")
as_data_frame("45D0501072")
```

   * Supplier Name: `MISSION AT AIR FORCE VILLAGE I, THE`
   * CCN: `45D0501072`
   * Supplier Type: `Laboratory`
   * Address: `4949 RAVENSWOOD DRIVE SAN ANTONIO, TX 78227`
   * Phone Number: `(210) 568-5162`
   * Participation Date: `1993-02-18`
   * Region: `(VI) Dallas`
   * Ownership Type: `Private`

```{r}
parse("14D2326049")
decode("14D2326049")
as_data_frame("14D2326049")
```

   * Supplier Name: `SCOTT AIR FORCE BASE OUTPATIENT CLINIC`
   * CCN: `14D2326049`
   * Supplier Type: `Laboratory`
   * Address: `310 W LOSEY ST SCOTT AIR FORCE BASE, IL 62225`
   * Phone Number: `(314) 652-4100`
   * Participation Date: `2025-06-26`
   * Region: `(V) Chicago`
   * Ownership Type: `Government - Federal`

```{r}
parse("05D0975224")
decode("05D0975224")
as_data_frame("05D0975224")
```

   * Supplier Name: `AIR FORCE VILLAGE WEST`
   * CCN: `05D0975224`
   * Supplier Type: `Laboratory`
   * Address: `17050 ARNOLD DR RIVERSIDE, CA 92518`
   * Phone Number: `(909) 697-2059`
   * Participation Date: `2000-06-29`
   * Region: `(IX) San Francisco`
   * Ownership Type: `Private`

