---
output: html_document
editor_options: 
  chunk_output_type: console
---

# CLIA

Laboratories that examine human specimens for the diagnosis, prevention, or
treatment of any disease or impairment of, or the assessment of the health of,
human beings are yet another category of suppliers and must meet Clinical
Laboratory Improvements of 1988 Act (CLIA) requirements.

```{r}
#| label: setup
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
library(provider)
source("code/gt_theme.R")
```

```{r}
#| label: api-clia
#| message: true
provider::clia(count = TRUE)
```

## Examples

- Name: `MISSION AT AIR FORCE VILLAGE I, THE`
- CCN: `45D0501072`
- Address: `4949 RAVENSWOOD DRIVE`
- City: `SAN ANTONIO`
- State: `TX`
- Zip: `78227`
- Cert: `1993-02-18`
- Region: `(VI) Dallas`
- Owner: `Private`

```{r}
provider::clia(ccn = "45D0501072") |> 
  dplyr::glimpse()
```

```{r}
parse("45D0501072")

decode("45D0501072")

as_data_frame("45D0501072") |> 
  dplyr::glimpse()
```

- Name: `SCOTT AIR FORCE BASE OUTPATIENT CLINIC`
- CCN: `14D2326049`
- Address: `310 W LOSEY ST`
- City: `SCOTT AIR FORCE BASE`
- State: `IL`
- Zip: `62225`
- Cert: `2025-06-26`
- Region: `(V) Chicago`
- Owner: `Government - Federal`

```{r}
provider::clia(ccn = "14D2326049") |> 
  dplyr::glimpse()
```

```{r}
parse("14D2326049")

decode("14D2326049")

as_data_frame("14D2326049") |> 
  dplyr::glimpse()
```

```{r}
provider::clia(ccn = "05D0975224") |> 
  dplyr::glimpse()
```

```{r}
parse("05D0975224")

decode("05D0975224")

as_data_frame("05D0975224") |> 
  dplyr::glimpse()
```

- Name: `AIR FORCE VILLAGE WEST`
- CCN: `05D0975224`
- Address: `17050 ARNOLD DR`
- City: `RIVERSIDE`
- State: `CA`
- Zip: `92518`
- Cert: `2000-06-29`
- Region: `(IX) San Francisco`
- Owner: `Private`
