---
output: html_document
editor_options: 
  chunk_output_type: console
---

# IPPS-Excluded Units

> Hospital Units Excluded From the Inpatient Prospective Payment System (IPPS)

An alpha character in the third position of the CCN identifies either hospitals
with swing-bed approval, rehabilitation units, or psychiatric units excluded
from PPS payment.

The third position (which is alpha) identifies the type of unit or swing-bed
designation. The last 3 digits must be exactly the same as the last 3 digits of
the parent provider.

```{r}
#| label: setup
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
library(cheapr)
```

The RO assigns the following alpha-characters in the third position as
indicated:

```{r}
#| label: unit_types
ccn::unit_types |>
  gt::gt() |>
  gt::tab_options(
    table.width = gt::pct(100),
    quarto.disable_processing = TRUE
  ) |>
  gtExtras::gt_theme_nytimes() |>
  gt::tab_style(
    style = gt::cell_text(
      font = gt::google_font(name = "JetBrains Mono"),
      color = "grey30",
      size = "small"
    ),
    locations = gt::cells_body(columns = gt::everything())
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(columns = abbr)
  ) |>
  gt::tab_style(
    style = gt::cell_text(color = "grey50", size = "small"),
    locations = gt::cells_body(columns = desc)
  )
```

## IPPS-Excluded Subunits

```{r}
#| label: subunit_types
ccn::subunit_types |>
  gt::gt() |>
  gt::tab_options(
    table.width = gt::pct(100),
    quarto.disable_processing = TRUE
  ) |>
  gtExtras::gt_theme_nytimes() |>
  gt::tab_style(
    style = gt::cell_text(
      font = gt::google_font(name = "JetBrains Mono"),
      color = "grey30",
      size = "small"
    ),
    locations = gt::cells_body(columns = gt::everything())
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(columns = abbr)
  ) |>
  gt::tab_style(
    style = gt::cell_text(color = "grey50", size = "small"),
    locations = gt::cells_body(columns = prefix)
  )
```


### Subunit Examples

```{r}
aff <- ccn:::get_pin("aff")

aff$fac |>
  collapse::fcount(facility_type) |>
  collapse::roworder(-N)

aff$sub |>
  collapse::fcount(facility_type) |>
  collapse::roworder(-N)

aff$fac[cheapr::which_(aff$sub$parent %in_% aff$fac$ccn), ] |>
  collapse::fcount(facility_type) |>
  collapse::roworder(-N)

aff$fac
aff$sub
```