---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Emergency Hospitals

```{r setup}
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
source("code/gt_theme.R")
# c(
#   "45D0501072",
#   "14D2326049",
#   "05D0975224",
#   "02012F",
#   "02011F",
#   "04008F",
#   "04013F",
#   "03006F"
#   )
```

CCNs assigned to Emergency Hospitals (both Federal and non-Federal) that do not
participate in the Medicare program.

Emergency hospitals are identified by a 6-position alphanumeric CCN. Positions
one and two identify the state in which the hospital is located. Position six,
an alpha character, identifies whether the hospital is Federal (`F`) or
non-Federal (`E`). Positions three, four and five represent a sequence beginning
with `001`. This sequence identifies the order, by state, in which the CCN was
issued.

For example, the CCN of the 34th emergency hospital in Maryland would be `21034E`.
The Regional Office assigns the CCN in strict numerical sequence without regard
to the Federal or non-Federal status.

## Example

```{r}
# USAF Hospital (Moody)
parse("11038F")
decode("11038F")
as_data_frame("11038F") |> str()
```

   * Provider Name: `US AIR FORCE HOSP`
   * CCN: `11038F`
   * Provider Type: `Hospital`
   * Address: `3278 MITCHELL BLVD, BLD 900 VALDOSTA, GA 31601`
   * Phone: `(229) 257-2778`
   * Participation Date: `1991-03-01`
   * Region: `(IV) Atlanta`
   * Accreditation Type: `Non-Accredited`
   * Number of Certified Beds: `38`
   * Ownership Type: Unrecognized Hospital Ownership (`CNTL_TYPE_CD = 0`)
   * Subtype: `00`

```{r}
parse("45D0501072")
decode("45D0501072")
as_data_frame("45D0501072")
```

   * Supplier Name: `MISSION AT AIR FORCE VILLAGE I, THE`
   * CCN: `45D0501072`
   * Supplier Type: `Laboratory`
   * Address: `4949 RAVENSWOOD DRIVE SAN ANTONIO, TX 78227`
   * Phone Number: `(210) 568-5162`
   * Participation Date: `1993-02-18`
   * Region: `(VI) Dallas`
   * Ownership Type: `Private`

```{r}
parse("14D2326049")
decode("14D2326049")
as_data_frame("14D2326049")
```

   * Supplier Name: `SCOTT AIR FORCE BASE OUTPATIENT CLINIC`
   * CCN: `14D2326049`
   * Supplier Type: `Laboratory`
   * Address: `310 W LOSEY ST SCOTT AIR FORCE BASE, IL 62225`
   * Phone Number: `(314) 652-4100`
   * Participation Date: `2025-06-26`
   * Region: `(V) Chicago`
   * Ownership Type: `Government - Federal`

```{r}
parse("05D0975224")
decode("05D0975224")
as_data_frame("05D0975224")
```

   * Supplier Name: `AIR FORCE VILLAGE WEST`
   * CCN: `05D0975224`
   * Supplier Type: `Laboratory`
   * Address: `17050 ARNOLD DR RIVERSIDE, CA 92518`
   * Phone Number: `(909) 697-2059`
   * Participation Date: `2000-06-29`
   * Region: `(IX) San Francisco`
   * Ownership Type: `Private`

```{r}
parse("02012F")
decode("02012F")
as_data_frame("02012F")
```

   * Provider Name: `US AIR FORCE HOSP`
   * CCN: `02012F`
   * Provider Type: `Hospital`
   * Address: `ELLISTON AFB APO 937 SEATTLE WASH FAIRBANKS, AK 99702`
   * Participation Date: `1991-03-01`
   * Region: `(X) Seattle`
   * Ownership Type: `Unrecognized Hospital Ownership (CNTL_TYPE_CD = 0)`
   * Accreditation Type: 	`Non-Accredited`
   * Number of Certified Beds: 	`20`
   * Subtype: `00`

