---
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
library(provider)
```

# ERH
Any nonparticipating hospital meeting the definition of an emergency hospital
for Medicare purposes may claim payment for emergency inpatient and outpatient
diagnostic services furnished to Medicare patients. There are six statutory
requirements that a hospital must meet to qualify as an emergency hospital
(§1861(e)(1), (2), (3), (4), (5), and (7)).

The hospital must:

- Be primarily engaged in providing, by or under the supervision of physicians, to inpatients, diagnostic and therapeutic services or rehabilitation services;
- Maintain clinical records on all patients;
- Have bylaws in effect with respect to its staff of physicians;
- Have a requirement that every patient must be under the care of a physician;
- Provide 24-hour nursing service rendered or supervised by a registered
professional nurse and have a licensed, practical, or registered professional
nurse on duty at all times; and,
- Be licensed or meet standards for licensing pursuant to State and local law.

## 'Emergency Hospital Services' Only

Emergency Hospitals (both Federal and non-Federal) that do not
participate in the Medicare program are identified by a 6-position alphanumeric CCN. Positions
one and two identify the state in which the hospital is located. Position six,
an alpha character, identifies whether the hospital is Federal (`F`) or
non-Federal (`E`). Positions three, four and five represent a sequence beginning
with `001`. This sequence identifies the order, by state, in which the CCN was
issued.

For example, the CCN of the 34th emergency hospital in Maryland would be
`21034E`. The Regional Office assigns the CCN in strict numerical sequence
without regard to the Federal or non-Federal status.

## Examples

```{r}
#| label: veterans
#| message: true
provider::veteran(count = TRUE)
provider::veteran(ccn = provider::contains("F"))
```

```{r}
#| label: hospital
#| message: true
provider::hospital(ccn = provider::ends("E")) |> str()
provider::hospital(ccn = provider::ends("F")) |> str()
```

