---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Emergency Hospitals

```{r setup}
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
```

CCNs assigned to Emergency Hospitals (both Federal and non-Federal) that do not
participate in the Medicare program.

Emergency hospitals are identified by a 6-position alphanumeric CCN. Positions
one and two identify the state in which the hospital is located. Position six,
an alpha character, identifies whether the hospital is Federal (`F`) or
non-Federal (`E`). Positions three, four and five represent a sequence beginning
with `001`. This sequence identifies the order, by state, in which the CCN was
issued.

For example, the CCN of the 34th emergency hospital in Maryland would be 21034E.
The Regional Office assigns the CCN in strict numerical sequence without regard
to the Federal or non-Federal status.

## Example

```{r}
parse("21034E")
decode("12345F")
as_data_frame("11038F") # USAF Hospital (Moody)
```


