---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Emergency Hospitals

```{r setup}
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
c(
  "45D0501072",
  "14D2326049",
  "05D0975224",
  "02012F",
  "02011F",
  "04008F",
  "04013F",
  "03006F"
  )
```

CCNs assigned to Emergency Hospitals (both Federal and non-Federal) that do not
participate in the Medicare program.

Emergency hospitals are identified by a 6-position alphanumeric CCN. Positions
one and two identify the state in which the hospital is located. Position six,
an alpha character, identifies whether the hospital is Federal (`F`) or
non-Federal (`E`). Positions three, four and five represent a sequence beginning
with `001`. This sequence identifies the order, by state, in which the CCN was
issued.

For example, the CCN of the 34th emergency hospital in Maryland would be 21034E.
The Regional Office assigns the CCN in strict numerical sequence without regard
to the Federal or non-Federal status.

## Example

```{r}
parse("21034E")
decode("12345F")
as_data_frame("11038F") # USAF Hospital (Moody)
```


   * Provider or Supplier Name: `US AIR FORCE HOSP`
   * CMS Certification Number: `11038F`
   * Provider or Supplier Type: `Hospital`
   * Address: `3278 MITCHELL BLVD, BLD 900 VALDOSTA, GA 31601`
   * Phone Number: `(229) 257-2778`
   * Participation Date: `1991-03-01`
   * Region: `(IV) Atlanta`
   * Accreditation Type: `Non-Accredited`
   * Number of Certified Beds: `38`
   * Ownership Type: Unrecognized Hospital Ownership (`CNTL_TYPE_CD = 0`)
   * Subtype: `00`


```{r}
"45D0501072"
```


Provider or Supplier Name: 	MISSION AT AIR FORCE VILLAGE I,, THE
CMS Certification Number: 	45D0501072
Provider or Supplier Type: 	Laboratory
Address: 	4949 RAVENSWOOD DRIVE
  	SAN ANTONIO, TX 78227
Phone Number: 	210 568-5162
Participation Date: 	02/18/1993
Region: 	(VI) Dallas
Ownership Type: 	Private


```{r}
"14D2326049"
```


Provider or Supplier Name: 	SCOTT AIR FORCE BASE OUTPATIENT CLINIC
CMS Certification Number: 	14D2326049
Provider or Supplier Type: 	Laboratory
Address: 	310 W LOSEY ST
  	SCOTT AIR FORCE BASE, IL 62225
Phone Number: 	314 652-4100
Participation Date: 	06/26/2025
Region: 	(V) Chicago
Ownership Type: 	Government - Federal 

```{r}
"05D0975224"
```


Provider or Supplier Name: 	AIR FORCE VILLAGE WEST
CMS Certification Number: 	05D0975224
Provider or Supplier Type: 	Laboratory
Address: 	17050 ARNOLD DR
  	RIVERSIDE, CA 92518
Phone Number: 	909 697-2059
Participation Date: 	06/29/2000
Region: 	(IX) San Francisco
Ownership Type: 	Private 

```{r}
"02012F"
```

Provider or Supplier Name: 	US AIR FORCE HOSP
CMS Certification Number: 	02012F
Provider or Supplier Type: 	Hospital
Address: 	ELLISTON AFB APO 937 SEATTLE WASH
  	FAIRBANKS, AK 99702
Phone Number: 	
Participation Date: 	03/01/1991
Region: 	(X) Seattle
Accreditation Type: 	Non-Accredited
Number of Certified Beds: 	20
Ownership Type: 	Unrecognized Hospital Ownership (CNTL_TYPE_CD = 0)
Subtype: 	00 