---
output: html_document
editor_options: 
  chunk_output_type: console
---

# HHA

```{r}
#| label: setup
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
library(provider)
```

```{r}
#| label: pin
#| message: false
ccn:::get_pin("hha") |>
  collapse::roworder(ccn)
```

```{r}
#| label: provider
#| message: true
provider::facility(fac_type = "HHA", count = TRUE)
provider::facility(fac_type = "HHA")
```

Section 1861(o) of the Act defines an HHA as an agency or organization which:

- Is primarily engaged in providing skilled nursing services and other therapeutic services;
- Has policies established by a group of professionals (associated with the agency or
organization), including one or more physicians and one or more registered
professional nurses, to govern the services which it provides;
- Provides for supervision of above-mentioned services by a physician or registered
professional nurse;
- Maintains clinical records on all patients;
- Is licensed pursuant to State or local law, or has approval as meeting the standards
established for licensing by the State or locality;
- Has in effect an overall plan and budget for institutional planning;
- Meets the CoPs in the interest of the health and safety of individuals who are furnished services by the HHA; and
- Meets additional requirements as the Secretary finds necessary for the effective
and efficient operation of the program.

For purposes of Part A home health services under Title XVIII, the term “home
health agency” does not include any agency or organization which is primarily
for the care and treatment of mental diseases.

The CoPs for a Medicare-approved HHA found in 42 CFR Part 484 are also based on
§1891 of the Act. These CoPs are listed in Appendix B, Interpretive Guidelines
for HHAs. Section 1891 of the Act requires, among other things, that the HHA:

- Protect and promote the rights of each individual under its care;
- Disclose ownership and management information required under the Act;
- Not use as a home health aide (on a full-time, temporary, per diem, or other basis)
any individual to provide items and services described in §1861(m) of the Act,
unless the individual has completed a training and competency evaluation program
(CEP) or a CEP that meets minimum standards established by the Secretary, and is
competent to provide such items and services;
- Operate and provide services in compliance with all applicable Federal, State, and
local laws and regulations (including the requirements of §1124 of the Act);
- Operate and provide services in compliance with accepted professional standards
and principles which apply to professionals providing items and services for the
HHA;
- Include an individual’s plan of care (PoC) required under §1861(m) of the Act as
part of the clinical record described in §1861(o)(3) of the Act; and
- Comply with the requirements of §1866(f) of the Act relating to maintaining
written policies and procedures respecting advance directives.

## Types of Agencies

An HHA may be a public, nonprofit or proprietary agency or a subdivision of such
an agency or organization.

1. Public agency is an agency operated by a State or local government. Examples
include State-operated HHAs and county hospitals. For regulatory purposes,
“public” means “governmental.” 2. Nonprofit agency is a private (i.e.,
nongovernmental) agency exempt from Federal income taxation under §501 of the
Internal Revenue Code of 1954. These HHAs are often supported, in part, by
private contributions or other philanthropic sources, such as foundations.
Examples would include non-profit visiting nurse associations or non-profit
hospitals. 3. Proprietary agency is a private, profit-making agency or
profit-making hospital.

# Hospice

```{r}
#| label: provider2
#| message: true
provider::facility(fac_type = "Hospice", count = TRUE)
provider::facility(fac_type = "Hospice")
```

A hospice is a public agency or private organization or a subdivision of either
of these that is primarily engaged in providing care and services to terminally
ill individuals, meets the CoPs for hospices, and has a valid Medicare provider
agreement. The law governing the provision of Medicare hospice services is found
at Section 1861(dd) of the Act. The law further clarifies that “terminally ill
individuals” are individuals having a “medical prognosis that the individual’s
life expectancy is 6 months or less.” This definition is further clarified at 42
CFR 418.3 to provide for a life expectancy of 6 months or less “if the illness
runs its normal course.”

Although the law does not explicitly define its expectations for “primarily
engaged,” CMS has interpreted it to mean exactly what it says, that a hospice
provider must be primarily engaged in providing hospice care and services
(Section 1861(dd)(2)(A)(i)). “Primarily” does not mean “exclusively.” This
requirement does not preclude the hospice from providing services to terminally
ill individuals who have not elected the hospice benefit or providing services
to individuals who are not terminally ill, as long as the primary activity of
the hospice is the provision of hospice services to terminally ill individuals
and the hospice meets all requirements for participation in Medicare.


## Hospice Benefit Periods

An individual may elect to receive Medicare hospice benefits for two periods of 90 days
and an unlimited amount of periods for 60 days each. (See 42 CFR 418.21.)

## Eligibility Requirements

In order to be eligible to elect hospice care under Medicare, an individual must be entitled
to Part A of Medicare and be certified as being terminally ill. (See 42 CFR 418.20.) An
individual is considered to be terminally ill if the individual has a medical prognosis that
his or her life expectancy is 6 months or less if the illness runs its normal course.
Referrals may come from any source, but patients must be assessed by the hospice
medical director for appropriateness of admission in consultation with the patient’s
attending physician (if the individual has one). 

The hospice medical director must consider the diagnosis of the terminal
condition of the patient, other health conditions, whether related or unrelated
to the terminal illness, and current clinically relevant information supporting
all diagnoses. The medical director may consult with the attending physician
directly or through information obtained indirectly. Information could be
obtained through the hospice nurse or others who would bring the attending
physician’s knowledge of the patient to the medical director when the admission
decision is being made.

The hospice must obtain written certification of terminal illness within 2
calendar days for each of the benefit periods listed in 42 CFR 418.21, even if a
single election continues in effect for an unlimited number of periods. If the
hospice cannot obtain the written certification within 2 calendar days, after a
period begins, it must obtain oral certification within 2 calendar days and
written certification before a claim for payment is submitted.

For the initial 90-day period, certification of terminal illness must be
obtained from the medical director of the hospice or the physician member of the
hospice interdisciplinary group (IDG) and the individual’s attending physician
(if the individual has one). Recertification for subsequent periods only
requires the certification of the hospice medical director or the physician
member of the IDG. Certification statements must be on file and dated by the
physician before the hospice submits a claim for payment. (See 42 CFR 418.22.)

### Description

Hospice care means a comprehensive set of services described in
Section1861(dd)(1) of the Act, identified and coordinated by the individual’s
attending physician, medical director and by an interdisciplinary group to
provide for the physical, psychosocial, spiritual and emotional needs of a
terminally ill patient and family members, as delineated in a specific patient
plan of care.

Hospice uses an interdisciplinary approach to caring for terminally ill
individuals that stresses palliative care as opposed to curative care.
Palliative care means patient and family-centered care that optimizes quality of
life by anticipating, preventing, and treating suffering. Palliative care
throughout the continuum of illness involves addressing physical, intellectual,
emotional, social, and spiritual needs and facilitating patient autonomy, access
to information, and choice.

The emphasis of hospice care is on effective symptom management, with the goal
of making the patient as physically and emotionally comfortable as possible, and
enabling the patient to remain at home as long as possible with minimal
disruption to normal activities. Counseling and respite services are available
to the family of the hospice patient. Hospice considers both the patient and the
family as the unit of care.

Although some hospices are located as part of a hospital, skilled nursing
facility (SNF), and home health agency (HHA), hospices must meet specific CoPs
and be separately certified and approved for Medicare participation as a hospice
provider of services. (See Exhibit 129 for “Hospice Survey and Deficiencies
Report,” Form CMS-643, and Exhibit 72 for “Hospice Request for Certification in
the Medicare Program,” Form CMS-417.)

### Hospice Core Services

With the exception of physician services, substantially all core services must
be provided directly by hospice employees on a routine basis. These services
must be provided in a manner consistent with acceptable standards of practice.
The following are hospice core services:

- Physician services;
- Nursing services, (routinely available and/or on call on a 24-hour basis, 7 days a
week) provided by or under the supervision of a registered nurse (RN)
functioning within a plan of care developed by the hospice (IDG) in consultation
with the patient’s attending physician, if the patient has one;
- Medical social services by a qualified social worker under the direction of a
physician; and
- Counseling (including, but not limited to, bereavement, dietary, and spiritual
counseling) with respect to care of the terminally ill individual and adjustment
to death. The hospice must make bereavement services available to the family and
other individuals identified in the bereavement plan of care up to 1 year
following the death of the patient.

The hospice may contract for physician services as specified in 42 CFR
418.64(a). A hospice may use contracted staff, if necessary, to supplement
hospice employees in order to meet the needs of patients under extraordinary or
other non-routine circumstances.

When the hospice provides inpatient care directly, it may do so either in space
that it owns or leases or in space shared with a Medicare certified hospital,
SNF, or Medicaid certified nursing facility (NF).

- If the hospice provides care in its own inpatient facility, the care may be provided
in space that the hospice either owns or leases from another facility or
building. The inpatient unit may consist of several beds, a group of beds, or a
wing and must meet all applicable Federal and State requirements and be surveyed
for compliance with 42 CFR 418.110 prior to providing inpatient care to
patients. This survey includes a Life Safety Code survey (which has currently
adopted the 2000 edition of the Life Safety Code of the National Fire Protection
Association) that must be done both at the time of initial certification of the
inpatient facility and at the time of recertification surveys.
- If the hospice provides care directly with hospice staff in space shared with a
Medicare-certified Hospital, SNF, or a Medicaid certified NF (for respite care
only), the SA reviews the agreement and patient files for compliance with 42 CFR
418.110(b) and 42 CFR 418.110(e) since the location already meets the remaining
requirements of 42 CFR 418.110 as a Medicare/Medicaid participating facility.
