---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Implementation

```{r setup}
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(vctrs)
library(rlang)
library(zeallot)
library(ccn)
ccn_examples <- ccn:::get_pin("ccn")
```

## `ccn` class

In this section, I’ll make a `ccn` class, i.e., a character vector that is printed as a CCN. We start by defining a low-level [constructor](https://adv-r.hadley.nz/s3.html#s3-constrcutor) to check types and/or sizes and call `new_vctr()`.

`ccn` is built on a character vector of any length and doesn’t have any attributes.


```{r}
#| label: new_ccn
new_ccn <- function(x = character()) {
  if (!is_character(x)) {
    abort("`x` must be a character vector.")
  }
  new_vctr(x, class = "ccn")
}

x <- new_ccn(ccn_examples[1:25])

x

str(x)
```

We then follow up with a user friendly helper. Here we’ll use `vec_cast()` to allow it to accept anything coercible to a character:

```{r}
#| label: ccn-cast
ccn <- function(x = character()) {
  x <- vec_cast(x, character())
  new_ccn(x)
}
```

Before you go on, check that user-friendly constructor returns a zero-length vector when called with no arguments. This makes it easy to use as a prototype.

```{r}
#| label: ccn-prototype
new_ccn()
ccn()
```

For the convenience of your users, consider implementing an is_percent() function:

```{r}
#| label: ccn-inherits
is_ccn <- function(x) {
  inherits(x, "ccn")
}
```

## `format()` method

The first method for every class should almost always be a `format()` method. This should return a character vector the same length as x. The easiest way to do this is to rely on one of R’s low-level formatting functions like `formatC()`:

```{r}
format.ccn <- function(x, ...) {
  out <- formatC(vec_data(x))
  out[is.na(x)] <- NA
  out
}

x <- ccn(ccn_examples[1:25])

x
```

(Note the use of `vec_data()` so `format()` doesn’t get stuck in an infinite loop, and that I take a little care to not convert `NA` to `"NA"`; this leads to better printing.)

The format method is also used by data frames, tibbles, and `str()`:

```{r}
data.frame(x)
```

For optimal display, I recommend also defining an abbreviated type name, which should be 4-5 letters for commonly used vectors. This is used in tibbles and in `str()`:

```{r}
vec_ptype_abbr.ccn <- function(x, ...) {
  "ccn"
}

tibble::tibble(x)

str(x)
```

If you need more control over printing in tibbles, implement a method for `pillar::pillar_shaft()`. See `vignette("pillar", package = "vctrs")` for details.

## Casting and coercion

The next set of methods you are likely to need are those related to coercion and casting. Coercion and casting are two sides of the same coin: changing the prototype of an existing object. When the change happens implicitly (e.g in c()) we call it coercion; when the change happens explicitly (e.g. with as.integer(x)), we call it casting.

One of the main goals of vctrs is to put coercion and casting on a robust theoretical footing so it’s possible to make accurate predictions about what (e.g.) c(x, y) should do when x and y have different prototypes. vctrs achieves this goal through two generics:

   - vec_ptype2(x, y) defines possible set of coercions. It returns a prototype if x and y can be safely coerced to the same prototype; otherwise it returns an error. The set of automatic coercions is usually quite small because too many tend to make code harder to reason about and silently propagate mistakes.
   - vec_cast(x, to) defines the possible sets of casts. It returns x translated to have prototype to, or throws an error if the conversion isn’t possible. The set of possible casts is a superset of possible coercions because they’re requested explicitly.
