---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Implementation

```{r}
#| label: setup
#| message: true
#| warning: true
#| error: true
#| echo: false
#| cache: false
#| comment: ""
library(vctrs)
library(rlang)
library(zeallot)
library(ccn)

in_between <- function(x, min, max) {
  (x - min) * (max - x) >= 0L
}

examples <- c(ccn:::get_pin("ccn"), "02", NA_character_)
```

## `ccn` Validation

```{r}
#| label: ccn_validation
#| error: true
is_valid_nchar <- function(x) {
  N <- collapse::vlengths(x)
  (N - 6L) * (14L - N) >= 0L
}

is_valid_nchar(examples[1:10])

all_valid_nchar <- function(x) {
  collapse::allv(is_valid_nchar(x), TRUE)
}

all_valid_nchar(examples)

which_not_valid_nchar <- function(x) {
  collapse::whichv(is_valid_nchar(x), FALSE)
}

which_not_valid_nchar(examples)
examples[which_not_valid_nchar(examples)]
```

## `ccn` Checks

```{r}
#| label: ccn_checks
#| error: true
check_valid_nchar <- function(
  x,
  arg = rlang::caller_arg(x),
  call = rlang::caller_env()
) {
  if (!all_valid_nchar(x)) {
    i <- which_not_valid_nchar(x)
    n <- length(i)
    cli::cli_abort(
      c(
        "{.strong {n}} Invalid {cli::qty(n)} CCN{?s}:",
        "x" = "{.val {x[i]}}"
      ),
      arg = arg,
      call = call
    )
  }
}

# check_valid_nchar(examples)

check_character <- function(
    x,
    arg = rlang::caller_arg(x),
    call = rlang::caller_env()
    ) {
  if (!is_character(x)) {
    cli::cli_abort(
      "`x` must be a character vector.",
      arg = arg,
      call = call
      )
  }
}
```


## `ccn` class

First, make a `ccn` class, i.e., a character vector that is printed as a `ccn`. Start by defining a low-level [constructor](https://adv-r.hadley.nz/s3.html#s3-constrcutor) to check types and/or sizes and call `new_vctr()`.

`ccn` is built on a character vector of any length and doesn’t have any attributes.


```{r}
#| label: new_ccn
#| error: true
new_ccn <- function(x = character()) {
  # check_character(x)
  # check_valid_nchar(x)
  new_vctr(x, class = "ccn")
}

x <- new_ccn(examples[1:25])

x

str(x)
```

We then follow up with a user friendly helper. Here we’ll use `vec_cast()` to allow it to accept anything coercible to a character:

```{r}
#| label: ccn-helper
#| error: true
ccn <- function(x = character()) {
  x <- vec_cast(x, character())
  new_ccn(x)
}
```

Before you go on, check that user-friendly constructor returns a zero-length vector when called with no arguments. This makes it easy to use as a prototype.

```{r}
#| label: ccn-prototype
#| error: true
new_ccn()
ccn()
```

For the convenience of your users, consider implementing an `is_ccn()` function:

```{r}
#| label: ccn-inherits
#| error: true
is_ccn <- function(x) {
  inherits(x, "ccn")
}
```

## `format()` method

The first method for every class should almost always be a `format()` method. This should return a character vector the same length as x. The easiest way to do this is to rely on one of R’s low-level formatting functions like `formatC()`:

```{r}
#| label: ccn-format
#| error: true
format.ccn <- function(x, ...) {
  out <- formatC(vec_data(x))
  out[is.na(x)] <- NA_character_
  out
}

# x <- ccn(examples[52000:52272])
x <- ccn(examples[1:2000])
x
```

(Note the use of `vec_data()` so `format()` doesn’t get stuck in an infinite loop, and that I take a little care to not convert `NA` to `"NA"`; this leads to better printing.)

The format method is also used by data frames, tibbles, and `str()`:

```{r}
#| label: ccn-data.frame
#| error: true
data.frame(x)
```

For optimal display, I recommend also defining an abbreviated type name, which should be 4-5 letters for commonly used vectors. This is used in tibbles and in `str()`:

```{r}
#| label: ccn-abbr
#| error: true
vec_ptype_abbr.ccn <- function(x, ...) {
  "ccn"
}

tibble::tibble(x)

str(x)
```

If you need more control over printing in tibbles, implement a method for `pillar::pillar_shaft()`. See `vignette("pillar", package = "vctrs")` for details.

## Casting and coercion

The next set of methods you are likely to need are those related to coercion and casting. Coercion and casting are two sides of the same coin: changing the prototype of an existing object. When the change happens implicitly (e.g in `c()`) we call it __coercion__; when the change happens explicitly (e.g. with `as.integer(x)`), we call it __casting__.

One of the main goals of __vctrs__ is to put coercion and casting on a robust theoretical footing so it’s possible to make accurate predictions about what (e.g.) `c(x, y)` should do when `x` and `y` have different prototypes. `vctrs` achieves this goal through two generics:

   - `vec_ptype2(x, y)` defines a possible set of __coercions__. It returns a prototype if `x` and `y` can be safely coerced to the same prototype; otherwise it returns an error. The set of automatic coercions is usually quite small because too many tend to make code harder to reason about and silently propagate mistakes.
   - `vec_cast(x, to)` defines the possible sets of __casts__. It returns `x` translated to have prototype `to`, or throws an error if the conversion isn’t possible. The set of possible casts is a _superset_ of possible __coercions__ because they’re requested explicitly.

### Double dispatch

Both generics use [double dispatch](https://en.wikipedia.org/wiki/Double_dispatch) which means that the implementation is selected based on the class of two arguments, not just one. __S3__ does not natively support double dispatch, so we implement our own dispatch mechanism. In practice, this means:

   - You end up with method names with two classes, like `vec_ptype2.foo.bar()`.
   - You don’t need to implement default methods (they would never be called if you do).
   - You can’t call `NextMethod()`.

### CCN class

We’ll make our `ccn` class coercible back and forth with character vectors.

`vec_ptype2()` provides a user friendly error message if the coercion doesn’t exist and makes sure `NA` is handled in a standard way. `NA` is technically a `logical` vector, but we want it to stand in for a missing value of any type.

```{r}
#| label: ccn-ptype2-1
#| error: true
vec_ptype2("bogus", ccn())
vec_ptype2(ccn(), NA)
vec_ptype2(NA, ccn())
```

By default and in simple cases, an object of the same class is compatible with itself:

```{r}
#| label: ccn-ptype2-2
#| error: true
vec_ptype2(ccn(), ccn())
```

However this only works if the attributes for both objects are the same. Also the default methods are a bit slower. It is always a good idea to provide an explicit coercion method for the case of identical classes. So we’ll start by saying that a `ccn` combined with a `ccn` yields a `ccn`, which we indicate by returning a prototype generated by the constructor.

```{r}
#| label: ccn-ptype2-3
#| error: true
vec_ptype2.ccn.ccn <- function(x, y, ...) new_ccn()
```

Next we define methods that say that combining a `ccn` and `character` should yield a `character`.

Because double dispatch is a bit of a hack, we need to provide two methods. It’s your responsibility to ensure that each member of the pair returns the same result: if they don’t you will get weird and unpredictable behaviour.

The double dispatch mechanism requires us to refer to the underlying type, `character`, in the method name. If we implemented `vec_ptype2.ccn.numeric()`, it would never be called.

```{r}
#| label: ccn-ptype2-4
#| error: true
vec_ptype2.ccn.character <- function(x, y, ...) character()
vec_ptype2.character.ccn <- function(x, y, ...) character()
```

We can check that we’ve implemented this correctly with `vec_ptype_show()`:

```{r}
#| label: ccn-ptype-show
#| error: true
vec_ptype_show(ccn(), character(), ccn())
```

The `vec_ptype2()` methods define which input is the richer type that `vctrs` should coerce to. However, they don’t perform any conversion. This is the job of `vec_cast()`, which we implement next. We’ll provide a method to cast a `ccn` to a `ccn`:

```{r}
#| label: ccn-cast
#| error: true
vec_cast.ccn.ccn <- function(x, to, ...) x
```

And then for converting back and forth between `character`s. To convert a `character` to a `ccn` we use the `ccn()` helper (not the constructor; this is un-validated user input). To convert a `ccn` to a `character`, we strip the attributes.

Note that for historical reasons the order of argument in the signature is the opposite as for `vec_ptype2()`. The class for `to` comes first, and the class for `x` comes second.

Again, the double dispatch mechanism requires us to refer to the underlying type, `character`, in the method name:

```{r}
#| error: true
vec_cast.ccn.character <- function(x, to, ...) ccn(x)
vec_cast.character.ccn <- function(x, to, ...) vec_data(x)
```

Then we can check this works with `vec_cast()`:

```{r}
#| error: true
vec_cast("030113", ccn())
vec_cast(ccn("030113"), character())
```

Once you’ve implemented `vec_ptype2()` and `vec_cast()`, you get `vec_c()`, `[<-`, and `[[<-` implementations for free.

```{r}
#| error: true
vec_c(ccn("030113"), "1")
vec_c(NA, ccn("030113"))
# but
vec_c(TRUE, ccn("030113"))

x <- ccn(examples[1:5])
x[1:2] <- LETTERS[1:5]
x[[3]] <- LETTERS[5]
x
```

