---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Preface {.unnumbered}

```{r setup}
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
source("code/gt_theme.R")
```

A __CMS Certification Number__ is a uniform way of identifying a healthcare
provider or supplier that has or currently does participate in the Medicare and/or Medicaid programs.

The __CCN__ is used to track provider agreements and cost reports. The __NPI__^[National
Provider Identifier] and __PTAN__^[Provider Transaction Account Number] are
tied to an entity's CCN. The __RO__^[CMS Regional Office] (not the __SA__^[State Agency] or __MAC__^[Medicare Administrative Contractor]) assigns the CCN and maintains adequate controls.

<br>

:::{.callout-important}

## One Term to Rule Them All

In [2007](https://www.cms.gov/medicare/provider-enrollment-and-certification/surveycertificationgeninfo/policy-and-memos-to-states-and-regions-items/cms1206256), the __CCN__ replaced the following terms: 

   * Medicare Provider Number
   * Medicare Identification Number
   * OSCAR Number^[Online Survey, Certification, and Reporting System.]

:::

## Canonical Format

A __*canonically valid* CCN__ is an alphanumeric string, either 6 or 10 characters in
length, that encodes a provider/supplier's state and facility type.

```{r}
#| label: canonical-ccns
#| echo: false
"670055" |>
  strsplit("") |>
  _[[1]] |>
  as.integer() |>
  rlang::set_names(1:6) |>
  as.list() |>
  list2DF() |>
  gt::gt() |>
  gt::fmt_integer(columns = gt::everything()) |>
  gt::tab_style(
    style = gt::cell_fill(
      color = "yellow",
      alpha = 0.4
    ),
    locations = gt::cells_body(columns = c(1:2))
  ) |>
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "red", alpha = 0.5),
      gt::cell_text(color = "white", weight = "bold")
    ),
    locations = gt::cells_body(columns = c(3:6))
  ) |>
  gt_chamber_theme()
```


## Providers Vs. Suppliers

Medicare differentiates between __providers__ and __suppliers__, the general
distinction being that providers are parties who care for patients awaiting,
receiving, or recuperating from treatment by intervening practitioners while
suppliers include those who furnish goods and services used in care and
treatment. 

Medicare providers and suppliers are defined at 42 CFR 498.2. In Medicare, as
specified in §1861(u) of the Social Security Act, providers include:

   - Hospitals
   - Critical Access Hospitals (CAHs)
   - Skilled Nursing Facilities (SNFs)
   - Home Health Agencies (HHAs)
   - Hospices
   - Comprehensive Outpatient Rehabilitation Facilities (CORFs)

Under §1835(a)(2) of the Act, clinics, rehabilitation agencies, or public health
agencies are included as providers if such clinic or agency meets the
requirements of §1861(p)(4)(A).

Community Mental Health Centers (CMHC) are providers of services for partial
hospitalization services only. Providers must meet CoPs or Requirements for SNFs
to participate in Medicare. (See definitions at 42 CFR 498.2.)


_Suppliers_ that must meet conditions for coverage/certification to participate
in Medicare are:

   - Portable X-Ray Services (PXRF)
   - End-Stage Renal Disease (ESRD) facilities
   - Ambulatory Surgical Centers (ASC)
   - Organ Procurement Organizations (OPO)
   - Rural Health Clinics (RHC)
   - Federally Qualified Health Centers (FQHC)
   - Laboratories (CLIA)

The above types of suppliers are distinguished from other suppliers, e.g.,
pharmacies, prosthesis suppliers, etc., for which there are no conditions for
coverage or certification, and which qualify for Medicare through the enrollment
process.

Medicaid, by contrast, uses __provider__ generically to include all health care
vendors. (See 42 CFR 431.107(a) and 433.37) and does not distinguish between
providers and suppliers. Section 1902(a)(27) of the Act provides for agreements
with every person or institution providing services under the State plan. 42 CFR
431.107(a) refers to all providers of services (including individual
practitioners and groups of practitioners).
