---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Preface

```{r setup}
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
source("code/gt_theme.R")
```

A __CMS Certification Number__ is a uniform way of identifying a healthcare
provider or supplier that has or currently does participate in the Medicare and/or Medicaid programs.

The __CCN__ is used to track provider agreements and cost reports. The __NPI__^[National
Provider Identifier] and __PTAN__^[Provider Transaction Account Number] are
tied to an entity's CCN. The __RO__^[CMS Regional Office] (not the __SA__^[State Agency] or __MAC__^[Medicare Administrative Contractor]) assigns the CCN and maintains adequate controls.


::: {.callout-tip}

## One Term to Rule Them All

In [2007](https://www.cms.gov/medicare/provider-enrollment-and-certification/surveycertificationgeninfo/policy-and-memos-to-states-and-regions-items/cms1206256), the __CCN__ replaced the following terms: 

   * Medicare Provider Number
   * Medicare Identification Number
   * OSCAR Number^[Online Survey, Certification, and Reporting System.]

:::

## Canonical Format

A __*canonically valid* CCN__ is an alphanumeric string, either 6 or 10 characters in
length, that encodes a provider/supplier's state and facility type.

```{r}
#| label: canonical-ccns
#| echo: false
"670055" |>
  strsplit("") |>
  _[[1]] |>
  as.integer() |>
  rlang::set_names(1:6) |>
  as.list() |>
  list2DF() |>
  gt::gt() |>
  gt::fmt_integer(columns = gt::everything()) |>
  gt::tab_style(
    style = gt::cell_fill(
      color = "yellow",
      alpha = 0.4
    ),
    locations = gt::cells_body(columns = c(1:2))
  ) |>
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "red", alpha = 0.5),
      gt::cell_text(color = "white", weight = "bold")
    ),
    locations = gt::cells_body(columns = c(3:6))
  ) |>
  gt_chamber_theme()
```


## Meaning of Providers and Suppliers

Medicare differentiates between __providers__ and __suppliers__, the
general distinction being that providers are parties who care for patients
awaiting, receiving, or recuperating from treatment by intervening
practitioners while suppliers include those who furnish goods and services
used in care and treatment. Medicaid terminology, by contrast, uses "provider"
generically to include all health care vendors. (See 42 CFR 431.107(a) and
433.37.)

Medicare providers and suppliers are defined at 42 CFR 498.2. In Medicare, as
specified in §1861(u) of the Social Security Act, providers include Hospitals,
Critical Access Hospitals (CAHs), Skilled Nursing Facilities (SNFs), Home Health
Agencies (HHAs), Hospices and Comprehensive Outpatient Rehabilitation Facilities
(CORFs). Under §1835(a)(2) of the Act, clinics, rehabilitation agencies, or
public health agencies are included as providers if such clinic or agency meets
the requirements of §1861(p)(4)(A). Community Mental Health Centers (CMHC) are
providers of services for partial hospitalization services only. Providers must
meet CoPs or Requirements for SNFs to participate in Medicare. (See definitions
at 42 CFR 498.2.)

Portable X-Ray Services, End-Stage Renal Disease (ESRD) facilities, Ambulatory
Surgical Centers (ASCs), and Organ Procurement Organizations (OPOs) are
_suppliers_ that must meet conditions for coverage to participate in Medicare.
Rural Health Clinics (RHCs) are suppliers that must meet conditions for
certification to participate in Medicare. Federally Qualified Health Centers
(FQHCs) are also recognized as suppliers of services and provide ambulatory care
services similar to those provided by RHCs. FQHCs may be located in urban, as
well as rural, areas. FQHCs are required to meet the same health and safety
standards as RHCs, with the exception of the certification procedures. FQHCs
self-attest to their compliance with Medicare conditions for coverage and are
only surveyed by CMS in connection with complaint investigations. The above
types of suppliers are distinguished from other suppliers, e.g., pharmacies,
prosthesis suppliers, etc., for which there are no conditions for coverage or
certification, and which qualify for Medicare through the enrollment process.

Laboratories that examine human specimens for the diagnosis, prevention, or
treatment of any disease or impairment of, or the assessment of the health of,
human beings are yet another category of suppliers and must meet Clinical
Laboratory Improvements of 1988 Act (CLIA) requirements. As previously stated,
Medicaid does not distinguish between providers and suppliers. Section
1902(a)(27) of the Act provides for agreements with every person or institution
providing services under the State plan. 42 CFR 431.107(a) refers to all
providers of services (including individual practitioners and groups of
practitioners).