---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Introduction

```{r setup}
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
source("code/gt_theme.R")
```

```{r}
#| label: pkg-version
#| echo: false
paste("ccn version:", sQuote(utils::packageVersion("ccn")), "loaded") |> cat()
```

A __CMS Certification Number__ is a uniform way of identifying a healthcare
provider or supplier that has or currently does participate in the Medicare and/or Medicaid programs.

The __CCN__ is used to track provider agreements and cost reports. The __NPI__^[National
Provider Identifier] and __PTAN__^[Provider Transaction Account Number] are
tied to an entity's CCN. The __RO__^[CMS Regional Office], not the __SA__^[State Agency] or __MAC__^[Medicare Administrative Contractor], assigns the CCN and maintains adequate controls.

::: {#tip-ccn .callout-tip}

## One Term to Rule Them All

In [2007](https://www.cms.gov/medicare/provider-enrollment-and-certification/surveycertificationgeninfo/policy-and-memos-to-states-and-regions-items/cms1206256), the __CCN__ replaced the following terms: 

   * Medicare Provider Number
   * Medicare Identification Number
   * OSCAR^[Online Survey, Certification, and Reporting System.] Number

:::

## Canonical Format

A __*canonically valid* CCN__ is an alphanumeric string, either 6 or 10 characters in
length, that encodes a provider/supplier's state and facility type.

```{r}
#| label: canonical-ccns
"670055" |>
  strsplit("") |>
  _[[1]] |>
  as.integer() |>
  rlang::set_names(1:6) |>
  as.list() |>
  list2DF() |>
  gt::gt() |>
  gt::fmt_integer(columns = gt::everything()) |>
  gt::tab_style(
    style = gt::cell_fill(
      color = "yellow",
      alpha = 0.4
    ),
    locations = gt::cells_body(columns = c(1:2))
  ) |>
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "red", alpha = 0.5),
      gt::cell_text(color = "white", weight = "bold")
    ),
    locations = gt::cells_body(columns = c(3:6))
  ) |>
  gt_chamber_theme()
```


