---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Introduction

```{r setup}
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""

library(ccn)
```

A __CMS Certification Number__ is a uniform way of identifying a healthcare
provider or supplier that has or currently does participate in the Medicare and/or Medicaid programs.

The CCN is used to track provider agreements and cost reports. The National
Provider Identifier (NPI) and Provider Transaction Account Number (PTAN) are
tied to an entity's CCN. The Regional Office (RO), not the State Agency (SA) or Medicare Administrative Contractor (MAC), assigns the CCN and maintains adequate controls.

::: {#note-mod .callout-note}

### One Term to Rule Them All

__CCN__ replaced the terms _Medicare Provider Number_, _Medicare Identification Number_ 
and _OSCAR Number_ in [2007](https://www.cms.gov/medicare/provider-enrollment-and-certification/surveycertificationgeninfo/policy-and-memos-to-states-and-regions-items/cms1206256).

:::

## Canonical Format

A __*canonically valid* CCN__ is an alphanumeric string, either 6 or 10 characters in
length, that encodes a provider/supplier's state and facility type.

## States

The first two characters of the CCN represent the state in which the provider or
supplier is located. 

```{r}
#| label: ccn-states
#| echo: false
#| message: false
ccn::states |>
  collapse::fgroup_by(abbr, name) |> 
  collapse::fsummarise(code = paste(code, collapse = ", ")) |> 
  gt::gt() |> 
  gtExtras::gt_theme_538(quiet = TRUE) |> 
  gt::tab_options(quarto.disable_processing = TRUE)
```

### Regional Offices

```{r}
#| label: ccn-regions
#| echo: false
#| message: false
ccn::regions |>
  collapse::sbt(!is.na(region), -ro) |> 
  collapse::frename(office = city) |>
  collapse::fgroup_by(region, office) |> 
  collapse::fsummarise(state = paste(state, collapse = ", ")) |> 
  gt::gt() |> 
  gtExtras::gt_theme_538(quiet = TRUE) |>
  gt::tab_options(quarto.disable_processing = TRUE)
```

