---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Medicaid-Only Providers

```{r setup}
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
```

## Facility Types

The last three characters of a Medicaid-Only Provider CCN represent the facility type and a unique
identifier. The facility type is encoded in the third character of the last four
characters. The table below summarizes the valid facility type codes and their
corresponding ranges. 

```{r}
#| label: medicaid-types
#| echo: false
#| message: false
ccn::medicaid_types |>
  collapse::fgroup_by(abbr, desc) |> 
  collapse::fsummarise(code = toString(code)) |> 
  gt::gt() |> 
  gt::tab_options(quarto.disable_processing = TRUE) |> 
  gtExtras::gt_theme_nytimes() |> 
  gt::tab_style(
    style = gt::cell_text(
      font = gt::google_font(name = "JetBrains Mono"), color = "grey60", size = "small"), 
    locations = gt::cells_body(columns = code)) |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"), 
    locations = gt::cells_body(columns = abbr)) |> 
  gt::tab_style(
    style = gt::cell_text(color = "grey50", size = "small"), 
    locations = gt::cells_body(columns = desc))
```

## Facility Ranges

The last three characters of a Medicaid-Only Provider CCN represent the facility type and a unique
identifier. The facility type is encoded in the third character of the last four
characters. The table below summarizes the valid facility type codes and their
corresponding ranges. 

```{r}
#| label: medicaid-ranges
#| echo: false
#| message: false
ccn::medicaid_ranges |>
  collapse::fgroup_by(abbr) |> 
  collapse::fsummarise(desc = toString(desc), range = toString(range)) |> 
  gt::gt() |> 
  gt::tab_options(quarto.disable_processing = TRUE) |> 
  gtExtras::gt_theme_nytimes() |> 
  gt::tab_style(
    style = gt::cell_text(
      font = gt::google_font(name = "JetBrains Mono"), color = "grey60", size = "small"), 
    locations = gt::cells_body(columns = range)) |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"), 
    locations = gt::cells_body(columns = abbr)) |> 
  gt::tab_style(
    style = gt::cell_text(color = "grey50", size = "small"), 
    locations = gt::cells_body(columns = desc))
```