---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Medicare

```{r setup}
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
source("code/gt_theme.R")
```

<br>

Providers and Suppliers paid under _Medicare Part A_ have __6 digit__ CCNs.
The first two characters represent the state in which the provider is located.
The last four characters identify the type of facility.

::: {.callout-tip}

## OPO Exception

Organ procurement organizations (OPOs) are assigned a 6-digit alphanumeric CCN.

   * The first 2 digits identify the State code. 
   * The third digit is the alpha character "P". 
   * The final 3 digits are the unique facility identifier.

:::

## Facility Ranges

The facility type is encoded in the third character of the last four
characters. The table below summarizes the valid facility type codes and their
corresponding ranges. 

```{r}
#| label: medicare-ranges
#| echo: false
#| message: false
ccn::medicare_ranges |>
  collapse::fgroup_by(abbr) |>
  collapse::fsummarise(
    desc = toString(desc), 
    range = toString(range)
    ) |>
  gt::gt() |>
  gt::tab_options(quarto.disable_processing = TRUE) |>
  gtExtras::gt_theme_nytimes() |>
  gt::tab_style(
    style = gt::cell_text(
      font = gt::google_font(name = "JetBrains Mono"),
      color = "grey60",
      size = "small"
    ),
    locations = gt::cells_body(columns = range)
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(columns = abbr)
  ) |>
  gt::tab_style(
    style = gt::cell_text(color = "grey50", size = "small"),
    locations = gt::cells_body(columns = desc)
  )
```
