---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Medicaid-Only

```{r}
#| label: setup
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
```

*Title XIX-Only* Providers are identified by a 6-position alphanumeric CCN.

## Facility Types

Position `3`, an alpha character, identifies the type of facility, either by
level or type of care being provided:

```{r}
#| label: medicaid-types
#| echo: false
#| message: false
ccn::medicaid_types |>
  collapse::fgroup_by(abbr, desc) |>
  collapse::fsummarise(code = toString(code)) |>
  gt::gt() |>
  gt::tab_options(
    table.width = gt::pct(100),
    quarto.disable_processing = TRUE
  ) |>
  gtExtras::gt_theme_nytimes() |>
  gt::tab_style(
    style = gt::cell_text(
      font = gt::google_font(name = "JetBrains Mono"),
      color = "grey60",
      size = "small"
    ),
    locations = gt::cells_body(columns = code)
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(columns = abbr)
  ) |>
  gt::tab_style(
    style = gt::cell_text(color = "grey50", size = "small"),
    locations = gt::cells_body(columns = desc)
  )
```

Positions `4`, `5` and `6` represent a sequence beginning with `001`.

## Medicaid-Only Hospitals

If position `3` is `J`, then the position `4`, `5` and `6` sequence identifies
the type of hospital:

```{r}
#| label: medicaid-ranges
#| echo: false
#| message: false
ccn::medicaid_ranges |>
  collapse::fgroup_by(abbr) |>
  collapse::fsummarise(
    desc = toString(desc),
    range = toString(range)
  ) |>
  gt::gt() |>
  gt::tab_options(
    table.width = gt::pct(100),
    quarto.disable_processing = TRUE
  ) |>
  gtExtras::gt_theme_nytimes() |>
  gt::tab_style(
    style = gt::cell_text(
      font = gt::google_font(name = "JetBrains Mono"),
      color = "grey60",
      size = "small"
    ),
    locations = gt::cells_body(columns = range)
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(columns = abbr)
  ) |>
  gt::tab_style(
    style = gt::cell_text(color = "grey50", size = "small"),
    locations = gt::cells_body(columns = desc)
  )
```

## MOH Example

```{r}
#| label: moh-examples
#| echo: false
#| message: false
ccn::parse("01J008")

ccn::decode("01J008")

purrr::map(c("01J008", "A5J508"), ccn::as_data_frame) |>
  collapse::rowbind(fill = TRUE) |>
  gt::gt() |>
  gtExtras::gt_theme_nytimes() |>
  gt::sub_missing() |>
  gt::tab_options(
    table.width = gt::pct(100),
    quarto.disable_processing = TRUE
  )
```

