---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Medicaid-Only

```{r}
#| label: setup
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
```

*Title XIX-Only* Providers are identified by a 6-position alphanumeric CCN.

## Facility Types

Position `3`, an alpha character, identifies the type of facility, either by
level or type of care being provided:

```{r}
#| label: medicaid-types
#| echo: false
#| message: false
ccn::medicaid_types |>
  collapse::fgroup_by(abbr, desc) |>
  collapse::fsummarise(code = toString(code)) |>
  gt::gt() |>
  gt::tab_options(
    table.width = gt::pct(100),
    quarto.disable_processing = TRUE
  ) |>
  gtExtras::gt_theme_nytimes() |>
  gt::tab_style(
    style = gt::cell_text(
      font = gt::google_font(name = "JetBrains Mono"),
      color = "grey60",
      size = "small"
    ),
    locations = gt::cells_body(columns = code)
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(columns = abbr)
  ) |>
  gt::tab_style(
    style = gt::cell_text(color = "grey50", size = "small"),
    locations = gt::cells_body(columns = desc)
  )
```

Positions `4`, `5` and `6` represent a sequence beginning with `001`.

## Medicaid-Only Hospitals

If position `3` is `J`, then the position `4`, `5` and `6` sequence identifies
the type of hospital:

```{r}
#| label: medicaid-ranges
#| echo: false
#| message: false
ccn::medicaid_ranges |>
  collapse::fgroup_by(abbr) |>
  collapse::fsummarise(
    desc = toString(desc),
    range = toString(range)
  ) |>
  gt::gt() |>
  gt::tab_options(
    table.width = gt::pct(100),
    quarto.disable_processing = TRUE
  ) |>
  gtExtras::gt_theme_nytimes() |>
  gt::tab_style(
    style = gt::cell_text(
      font = gt::google_font(name = "JetBrains Mono"),
      color = "grey60",
      size = "small"
    ),
    locations = gt::cells_body(columns = range)
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(columns = abbr)
  ) |>
  gt::tab_style(
    style = gt::cell_text(color = "grey50", size = "small"),
    locations = gt::cells_body(columns = desc)
  )
```

## MOH Example

```{r}
#| label: moh-examples
#| echo: false
#| message: false
ccn::parse("01J008")

ccn::decode("01J008")

purrr::map(c("01J008", "A5J508"), ccn::as_data_frame) |>
  collapse::rowbind(fill = TRUE) |>
  gt::gt() |>
  gtExtras::gt_theme_nytimes() |>
  gt::sub_missing() |>
  gt::tab_options(
    table.width = gt::pct(100),
    quarto.disable_processing = TRUE
  )
```

## Intermediate Care Facilities

An ICF/IID is an institution that meets Federal CoPs and has as its primary
purpose the provision of health or rehabilitation services to individuals with
intellectual disabilities or related conditions receiving care and services
under the Medicaid program.

The ICF/IID CoPs recognize the developmental, social, and behavioral needs of
individuals with intellectual disabilities who live in residential settings by
requiring that each individual both require and receive active treatment for the
ICF/IID care to be eligible for Medicaid funding.

Active treatment means the aggressive, consistent implementation of a program of
specialized and generic training, treatment, health, and related services
directed toward the acquisition of the behaviors necessary for the individual to
function with as much self-determination and independence as possible. It
includes the prevention or deceleration of regression or loss of current optimal
functional status.

### Distinct Part ICF/IID

Neither the law nor Federal regulations define or require ICF/IID services in
terms of distinct parts. However, as a State Medicaid program requirement,
States may provide for distinct part ICF/IID approvals. Where the SMA elects to
define the ICF/IID program in terms of distinct parts, these additional Federal
provisions must be met:

- The distinct part must be a clearly identified unit, such as an entire ward, wing,
floor, building, or a number of designated rooms;
- The distinct part consists of all beds and related facilities in the unit; and
- The institution does not need require transfer of patients or individuals to or from
the distinct part, where, in the opinion of the attending physician, transfer
might be harmful to the physical or mental health of the patient or individual.
Otherwise, the unit houses all ICF/IID residents in the institution.

