---
output: html_document
editor_options: 
  chunk_output_type: console
---

# OPO

```{r}
#| label: setup
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
library(provider)
x <- ccn:::get_pin("opo")
```

An **Organ Procurement Organization** performs or coordinates the procurement,
preservation, and transport of organs and maintains a system for locating
prospective recipients for available organs.

An OPO must have been certified as a qualified OPO by CMS under 42 U.S.C. 273(b)
and § 486.303 to be eligible for designation. In order to be certified as a
qualified OPO, an OPO must have received a grant under 42 U.S.C. 273(a) or have
been certified or re-certified by the Secretary within the previous four years
as being a qualified OPO. Under the statute, no new OPOs can enroll into the
Medicare program.

An OPO is designated for a 4-year agreement cycle. The period may be shorter,
for example, if an OPO has voluntarily terminated its agreement with CMS and CMS
selects a successor OPO for the balance of the 4-year agreement cycle.
Re-certification must occur not more frequently than once every 4 years. The SOG
Location is responsible for conducting the re-certification surveys every 4
years; the OPO must sign a new provider agreement (Form CMS-576A) and
participate in the Organ Procurement and Transplantation Network. (See CMS Pub.
100-07, chapter 2, sections 2810 and 2811.)

Organ procurement organizations (OPOs) are assigned a 6-digit alphanumeric CCN.
The first 2 digits identify the State code. The third digit is the alpha
character P. The remaining 3 digits are the unique facility identifier.

## OPOs

```{r}
x$opo_codes <- collapse::tfmv(x$opo_codes, "opo", toupper)
x$opo_county <- collapse::tfmv(x$opo_county, "county", toupper)
x$opo_county[cheapr::which_val(x$opo_county$code, "PRLL"), ]$state <- "PR"
x$opo_active <- collapse::tfmv(x$opo_active, "county", toupper)
x$opo_active <- collapse::ss(x$opo_active, j = c(1:3, 5:6), check = FALSE)

opo <- collapse::join(
  x$opo_codes, 
  x$opo_county, 
  on = "code", 
  verbose = 0L, 
  multiple = TRUE
) |> 
  collapse::join(
    x$opo_active, 
    on = c("opo" ,"state"), 
    verbose = 0L
  ) |> 
  fastplyr::f_fill(.cols = c("ccn", "region", "orig_date")) |>
  collapse::colorderv("ccn") |> 
  collapse::roworderv("ccn")

opo
```

### Codes

```{r}
#| label: opo-codes
cnty <- x$opo_county |>
  # collapse::slt(-code) |>
  collapse::roworder(state, county) |>
  collapse::fgroup_by(state, code) |>
  collapse::fsummarise(counties = length(county)) |>
  collapse::fungroup()

x$opo_codes$id <- cheapr::sequence_(nrow(x$opo_codes))

x$opo_codes |>
  collapse::colorder(id) |> 
  collapse::roworder(code) |>
  collapse::join(cnty, verbose = 0L, multiple = TRUE, on = "code") |>
  gt::gt() |>
  gt::tab_options(
    table.width = gt::pct(100),
    quarto.disable_processing = TRUE
  ) |>
  gtExtras::gt_theme_nytimes() |>
  gt::tab_style(
    style = gt::cell_text(
      font = gt::google_font(name = "JetBrains Mono"),
      color = "grey30",
      size = "small"
    ),
    locations = gt::cells_body(columns = gt::everything())
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(columns = c(code, state))
  ) |>
  gt::tab_style(
    style = gt::cell_text(color = "grey60"),
    locations = gt::cells_body(columns = c(id, opo))
  )
```

## Counties

```{r}
#| label: opo-county
cnty <- x$opo_county |>
  collapse::slt(-code) |>
  collapse::roworder(state, county) |>
  collapse::fgroup_by(state) |>
  collapse::fsummarise(counties = length(county)) |>
  collapse::fungroup()

x$opo_county |>
  collapse::slt(-county) |>
  collapse::funique() |>
  collapse::fgroup_by(state) |>
  collapse::fsummarise(codes = toString(code)) |>
  collapse::join(cnty, verbose = 0L) |>
  collapse::roworder(state) |>
  gt::gt() |>
  gt::tab_options(
    table.width = gt::pct(100),
    quarto.disable_processing = TRUE
  ) |>
  gtExtras::gt_theme_nytimes() |>
  gt::tab_style(
    style = gt::cell_text(
      font = gt::google_font(name = "JetBrains Mono"),
      color = "grey30",
      size = "small"
    ),
    locations = gt::cells_body(columns = c(codes, counties))
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(columns = state)
  ) |>
  gt::tab_style(
    style = gt::cell_text(color = "grey25"),
    locations = gt::cells_body(columns = state)
  )
```

### Active

```{r}
#| label: opo-active
#| echo: false
x$opo_active |>
  collapse::roworder(ccn) |>
  # collapse::slt(-region, -orig_date) |>
  gt::gt() |>
  gt::tab_options(
    table.width = gt::pct(100),
    quarto.disable_processing = TRUE
  ) |>
  gtExtras::gt_theme_nytimes() |>
  gt::tab_style(
    style = gt::cell_text(
      font = gt::google_font(name = "JetBrains Mono"),
      color = "grey30",
      size = "small"
    ),
    locations = gt::cells_body(columns = c(ccn, orig_date))
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(columns = state)
  ) |>
  gt::tab_style(
    style = gt::cell_text(color = "grey50", size = "small"),
    locations = gt::cells_body(columns = c(opo, region))
  )
```

## Approved Transplant Programs

### Procedure Types

```{r}
#| label: txc-types
#| echo: false
ccn:::get_pin("txc") |>
  collapse::slt(txc = txc_code, description = txc_type) |>
  collapse::funique() |>
  gt::gt() |>
  gt::tab_options(
    table.width = gt::pct(100),
    quarto.disable_processing = TRUE
  ) |>
  gtExtras::gt_theme_nytimes() |>
  gt::tab_style(
    style = gt::cell_text(
      font = gt::google_font(name = "JetBrains Mono"),
      color = "grey30",
      size = "small"
    ),
    locations = gt::cells_body(columns = txc)
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(columns = txc)
  ) |>
  gt::tab_style(
    style = gt::cell_text(color = "grey50", size = "small"),
    locations = gt::cells_body(columns = description)
  )
```

### Facilities

```{r}
#| label: txc-facs
#| echo: false
ccn:::get_pin("txc") |>
  collapse::slt(-txc_type) |>
  collapse::rnm(code = optn_code, txc = txc_code) |>
  collapse::funique() |>
  collapse::roworder(ccn, state, code) |>
  collapse::fgroup_by(ccn, state, code) |>
  collapse::fsummarise(txc = toString(txc)) |>
  collapse::fungroup() |>
  gt::gt() |>
  gt::tab_options(
    table.width = gt::pct(100),
    quarto.disable_processing = TRUE
  ) |>
  gtExtras::gt_theme_nytimes() |>
  gt::tab_style(
    style = gt::cell_text(
      font = gt::google_font(name = "JetBrains Mono"),
      color = "grey30",
      size = "small"
    ),
    locations = gt::cells_body(columns = c(ccn, txc))
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(columns = state)
  ) |>
  gt::tab_style(
    style = gt::cell_text(color = "grey50", size = "small"),
    locations = gt::cells_body(columns = code)
  )
```
