---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Providers

```{r setup}
#| message: false
#| warning: false
#| echo: false
#| cache: false
#| comment: ""
library(ccn)
```

```{r}
#| label: pkg-version
#| echo: false
paste("ccn version:", sQuote(utils::packageVersion("ccn")), "loaded") |> cat()
```

CCNs for Providers and Suppliers paid under _Medicare Part A_ have __6 digits__. The first two characters represent the state and the last four characters represent the facility type and a unique
identifier.

## Facility Ranges

The last four characters of a Provider CCN represent the facility type and a unique
identifier. The facility type is encoded in the third character of the last four
characters. The table below summarizes the valid facility type codes and their
corresponding ranges. 

```{r}
#| label: medicare-ranges
#| echo: false
#| message: false
ccn::medicare_ranges |>
  collapse::fgroup_by(abbr) |>
  collapse::fsummarise(
    desc = toString(desc), 
    range = toString(range)
    ) |>
  gt::gt() |>
  gt::tab_options(quarto.disable_processing = TRUE) |>
  gtExtras::gt_theme_nytimes() |>
  gt::tab_style(
    style = gt::cell_text(
      font = gt::google_font(name = "JetBrains Mono"),
      color = "grey60",
      size = "small"
    ),
    locations = gt::cells_body(columns = range)
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(columns = abbr)
  ) |>
  gt::tab_style(
    style = gt::cell_text(color = "grey50", size = "small"),
    locations = gt::cells_body(columns = desc)
  )
```
