---
output: html_document
editor_options: 
  chunk_output_type: console
---

# TXC

```{r}
#| label: setup
#| message: false
library(ccn)
library(collapse)
library(provider)
x <- ccn::decode_ccnr(ccn:::get_pin("hosp")$ccn)
x <- collapse::ss(x, x$facility %==% "TXC")$ccn
txc <- ccn:::get_pin("txc")
class(txc) <- setdiff(class(txc), "spec_tbl_df")
collapse::colorderv(txc, c("ccn", "state", "optn_code"))
```

## Approved Transplant Programs

```{r}
#| label: txc-types
#| echo: false
collapse::ss(txc, txc$ccn %iin% x) |> 
  gt::gt() |>
  gt::tab_options(
    table.width = gt::pct(100),
    quarto.disable_processing = TRUE
  ) |>
  gtExtras::gt_theme_nytimes() |>
  gt::tab_style(
    style = gt::cell_text(
      font = gt::google_font(name = "JetBrains Mono"),
      color = "grey30",
      size = "small"
    ),
    locations = gt::cells_body(columns = gt::everything())
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(columns = txc_code)
  ) |>
  gt::tab_style(
    style = gt::cell_text(color = "grey50", size = "small"),
    locations = gt::cells_body(columns = txc_type)
  )
```

## Organ Procurement and Transplantation Network (OPTN) 

The OPTN is a public-private partnership that links all professionals involved
in the donation and transplantation system. The OPTN operates the national
network for organ procurement and allocation and works to promote organ
donation. The OPTN was established by the National Organ Transplant Act of 1984
and is operated by United Network for Organ Sharing (UNOS) under a contract from
the Health Resources and Services Administration (HRSA) in accordance with
section 372 of the Public Health Service (PHS) Act. Through its policies, the
OPTN works to increase the number of transplants, provide equity in access to
transplants, improve outcomes for wait-listed patients, living donors, and
transplant recipients, and promote living donor and transplant recipient safety.
